Malacology: A Programmable Storage System Built on Ceph

### 2016-05-10 paper/paper.tex
new outline for sec 2
Signed-off-by: Noah Watkins <noahwatkins@gmail.com>
Update paper.tex
line 406: "In our current we"
line 724: update until each OSD makes the update live (the cost of the Paxos proposal is

By embedding the Lua runtime, Malacology makes the base RADOS API available in a 
dynamic environment, resulting in a object storage API with economy of 
expression, which at the same time provides the full set of features of the base 
object class. New object interfaces that are expressed in thousands of lines of 
code can be implemented in approximately an order of magnitude less 
code~\cite{geambasu_comet_2010}.

@@

\paragraph*{Malacology:} Metadata service policies and object storage interfaces are stored durability
within RADOS and managed by storing references with the object maps. Since
the cluster already propagates a consistent view of these data structures,
we use this service to automatically install interfaces in OSDs, and install
policies within the MDS such that clients and daemons are synchronzied on
correct implementations without restarting.

@@

{\bf Capability policies.}
We use capabilitity policies in the metadata service to tune the amount of
time that clients may cache the sequencer resource. This allows us to control
the trade-off between latency and throughput beyond the standard best-effort
policy.

@@

While a best-effort approach to sharing capabilities makes sense for a file
system client, throughput drops significantly with two clients as the majority
of the time neither client has the capapbitility as it ping-pongs between
clients. This observation reveals a tuning parameter: how long a client
maintains its capapbility lease. In throughputs labeled $2C,<time>$ we show
aggregate throughput as we decrease the amount of time that a client holds its
lease before responding to a request for the capapbility.  At lease times as
low as 10ms throughputs achieve a significant proportion of the locally cached
throughput.

While the batching mechanism can achieve high-throughput, it is not appropriate
for applications that require predictable latency. The throughput in
Figure~\ref{fig:captp} labeled $2C,ZLog$ corresponds to a centeralized
sequencer implementation. While throughput is lower for two clients (because of
the synchronous network round-trip required for each request),
Figure~\ref{fig:capcdf} shows that this approach achieves more predicable
latency compared to all other approaches except for the single client locally
cached mode.

@@

Programmable storage is a viable method for eliminating duplication of
complex error prone software that are used as workarounds for storage
system deficiencies. However, this duplication has real-world problems
related to reliability. We propose that system expose their services in
a safe way allowing application developers to customize system behavior
to meet their needs while not sacrificing correctness.

We are intend to pursue this work towards the goal of constructing a set
of customization points that allow a wide variety of storage system
services to be configured on-the-fly in existing systems. This work is
one point along that path in which we have looked an a target
special-purpose storage system. Ultimately we want to utilize
declarative methods for expressing new services.

>>>>

By embedding the Lua runtime, Malacology makes the base RADOS API available in a 
dynamic environment, resulting in an object storage API with economy of 
expression, which at the same time provides the full set of features of the base 
object class. New object interfaces that are expressed in thousands of lines of 
code can be implemented in approximately an order of magnitude less 
code~\cite{geambasu_comet_2010}.

@@

\paragraph*{Malacology:} Metadata service policies and object storage interfaces are stored durably
within RADOS and managed by storing references with the object maps. Since
the cluster already propagates a consistent view of these data structures,
we use this service to automatically install interfaces in OSDs, and install
policies within the MDS such that clients and daemons are synchronzied on
correct implementations without restarting.

@@

{\bf Capability policies.}
We use capability policies in the metadata service to tune the amount of
time that clients may cache the sequencer resource. This allows us to control
the trade-off between latency and throughput beyond the standard best-effort
policy.

@@

While a best-effort approach to sharing capabilities makes sense for a file
system client, throughput drops significantly with two clients as the majority
of the time neither client has the capability as it ping-pongs between
clients. This observation reveals a tuning parameter: how long a client
maintains its capability lease. In throughputs labeled $2C,<time>$ we show
aggregate throughput as we decrease the amount of time that a client holds its
lease before responding to a request for the capability.  At lease times as
low as 10ms throughputs achieve a significant proportion of the locally cached
throughput.

While the batching mechanism can achieve high-throughput, it is not appropriate
for applications that require predictable latency. The throughput in
Figure~\ref{fig:captp} labeled $2C,ZLog$ corresponds to a centralized
sequencer implementation. While throughput is lower for two clients (because of
the synchronous network round-trip required for each request),
Figure~\ref{fig:capcdf} shows that this approach achieves more predicable
latency compared to all other approaches except for the single client locally
cached mode.

@@

Programmable storage is a viable method for eliminating duplication of
complex error prone software that are used as workarounds for storage
system deficiencies. However, this duplication has real-world problems
related to reliability. We propose that systems expose their services in
a safe way, allowing application developers to customize system behavior
to meet their needs while not sacrificing correctness.

We are intend to pursue this work towards the goal of constructing a set
of customization points that allow a wide variety of storage system
services to be configured on-the-fly in existing systems. This work is
one point along that path in which we have looked at a target
special-purpose storage system. Ultimately we want to utilize
declarative methods for expressing new services.
